---
title: "**Importing Kivikuaka's data from movebank**"
author: Romain Lorrilliere\thanks{\href{mailto:romain.lorrilliere@mnhn.fr}{\textit{romain.lorrilliere@mnhn.fr}}}
date: "`r format(Sys.time(), '%d/%m/%Y %H:%M')`"
output:
  github_document:
    toc: true
    toc_depth: 2
    fig_width: 5
    fig_height: 5
    dev: jpeg    
  html_document:
    df_print: paged
    fig_height: 12
    fig_width: 16
    toc: yes
    toc_depth: 3
    toc_float:
      collapsed: true
      smooth_scroll: false
    number_sections: true
    code_folding: hide
    keep_md: true
pdf_document:
  toc: yes
  toc_depth: '1'
params: 
   set_rep: "C:/git/KiviKuaka/"
   set_file_data: "data/data_kivikuaka_events.csv"
   set_mb_user: "romainlorrilliere"
   set_mb_pw: "xxx"
   set_nb_day_before_fig: 20
   set_id_previous_import: "20210423_2017"
   set_save_fig: FALSE 
---

```{r setup, include=FALSE}

knitr::opts_chunk$set(echo =FALSE, eval=TRUE, message = FALSE, warning = FALSE,cache=FALSE)

```


```{r param_test}

rep <- params$set_rep
file_data <- params$set_file_data
pw <- params$set_mb_pw
username <- params$set_mb_user
save.fig <- params$set_save_fig
nb_day_before_fig   <- params$set_nb_day_before_fig
id_previous_import <- params$set_id_previous_import
if(id_previous_import == "xxx") id_previous_import <- NULL

```




```{r changeRep}

knitr::opts_knit$set(root.dir = rep)
#setwd("..")

```


```{r source}

file_source <- paste0(rep,"functions/fun_rmd_generic.r")
source(file_source)
file_source <- paste0(rep,"functions/fun_importation.r")
source(file_source)



```


# Get data from movebank



```{r movebank_log}

if(pw == "xxx"){
    file <- paste0(rep,"data/pw.txt")
    pw <- get_pw(file)
}
log <- movebankLogin(username,pw)
```



```{r last_date_import, echo=FALSE,warning=FALSE, message=FALSE}

last_import_date <- NULL
difftime_last_import <- NULL
txt_last_import <- "This is the first data importing."
if(!is.null(id_previous_import)) {
  previous_file <- paste0(rep,file_path_sans_ext(file_data),"_",id_previous_import,".csv")
  new_previous_file <- paste0(rep,file_data)
  file.copy(previous_file,new_previous_file,overwrite = TRUE, copy.date = TRUE)
}
  

if(basename(file_data) %in% dir(paste0(rep,"data/"))) {
  dlast <- fread(paste0(rep,file_data))
  if("db_date" %in% colnames(dlast)) { 
    last_import_date <- dlast[1,db_date] 
    difftime_last_import <- trunc(as.numeric(difftime(Sys.time(),last_import_date,units = "day")))
    txt_last_import <- paste0("Date of the previous data update: ",last_import_date," (",difftime_last_import," day(s))\n")
  } 
  file_save <- paste0(rep,file_path_sans_ext(file_data),ifelse(is.null(last_import_date),"",paste0("_",format(last_import_date,"%Y%m%d_%H%M"))),".csv")
  fwrite(dlast,file_save)
}

```


`r txt_last_import`


To import data of Kivi-Kuaka program from movebank website we use function from the move library. 
The id of the program in the movebank database is _1381110575_.


```{r movebank_import}
ind <- get_birds(con=log)
d <- get_events(con=log,id_previous_import = id_previous_import)
```

# Summary of update

## The birds


In French Polynesia, we deployed Icarus GPS 5g beacon on 56 birds of four species, three shorebirds (13 Bristle-thighed Curlew, 8 Pacific Golden Plover, 23 Wandering Tattler), and 12 Sooty Tern. 



```{r summary_ind}
summary_ind <- summary_new_ind(ind)

nb_birds <- sum(summary_ind$nb_birds)

nb_birds_5days <- sum(summary_ind$nb_birds_5days)
nb_birds_10days <- sum(summary_ind$nb_birds_10days)
nb_birds_15days <- sum(summary_ind$nb_birds_15days)

prop_5days <-  round(nb_birds_5days/nb_birds,2)
prop_10days <- round(nb_birds_10days/nb_birds,2)
prop_15days <- round(nb_birds_15days/nb_birds,2)

my_kable_print(summary_ind,caption="The summary of number of birds",scroll_width = "600px",scroll=FALSE)

```



Among these 56 birds, __`r nb_birds`__ birds with Icarus GPS beacons sent to at least one location. In the last fifteen days, __`r nb_birds_15days`__ beacons (`r round(prop_15days*100)`%) sent data, this number pass to __`r nb_birds_10days`__ beacons (`r round(prop_10days*100)`%) in the last ten days, and for the last five days, __`r nb_birds_5days`__ beacons (`r round(prop_5days*100)`%).




```{r fig.silence, fig.width=7, fig.height=7,eval=TRUE,fig.align = 'center', out.width='70%',fig.cap="Distrubiton of the number of days before after location by species",fig.scap="number of days before after location"}
ggplot_silence(ind)
```


## The new events


```{r summary_events}
nbline <- nrow(d)
nbloc <- nrow(d[!(is.na(location_lat))])

d_tax <- fread(paste0(rep,"data/taxon.csv"))
vec_tax_eng <- d_tax[taxon %in% unique(d$taxon),taxon_eng]
vec_tax<- d_tax[taxon %in% unique(d$taxon),taxon]

```

In the events database, there are `r nbline` data, but some do not have a valid location. 
There are __`r nbloc`__ data with location, that corresponds to `r round(nbloc/nbline * 100)`\%.


```{r summary_new_events}
  sne <- summary_new_events(d)
if(is.null(sne)) nb_new <- 0 else nb_new <- sum(sne$nb_new_events)
```

There `r ifelse(nb_new<1,"is","are")` __`r nb_new`__ new data since the last update `r ifelse(is.null(difftime_last_import),"",paste0(last_import_date," (",difftime_last_import," day(s))"))`. 


```{r summary_new_events_table,eval=FALSE, include=FALSE}
if(!(is.null(sne)))
  my_kable_print(sne,caption="The new events",scroll_width = "600px")
```

## The events by day

```{r title_fig_bird_day}
    cap_txt <- paste0("The bird locations by day for the ",vec_tax_eng," during the last 30 days")
```


```{r bird_day,echo=FALSE,warning=FALSE, message=FALSE,fig.width=9, fig.height=12,eval=TRUE,fig.align = 'center', out.width='100%', fig.cap=cap_txt}

data_by_day(d=d,ind=ind,vec_tax=vec_tax,nb_last_day=30,last_update_date = as.Date(last_import_date))

```

# The recent moves


````{r title_fig_bird_tracks}

dld <- d[difftime(date,as.Date(Sys.time()) - nb_day_before_fig  )> 0 & !is.na(location_lat),]

t_indld <- unique(dld[,.(bird_id,nick_name,taxon_eng)])
setorder(t_indld,bird_id)

txt_nn <- paste0(ifelse(t_indld[,nick_name] == "",""," named "),t_indld[,nick_name])

cap_txt <- paste0("The last ten days moves of the ",t_indld[,taxon_eng]," ",t_indld[,bird_id],txt_nn,". Yellow dots for the new locations")


```





``` {r tracks_birds,eval=TRUE ,echo=FALSE,warning=FALSE, message=FALSE, fig.width=7, fig.height=7,fig.align = 'center', out.width='100%', fig.cap=cap_txt}
bird_tracks_new(d,nb_last_day=nb_day_before_fig,date_last_update = as.Date(last_import_date),margin=.5)
```



# The data base

## The birds


```{r movebankdata_ind}
ind_select <- ind[,.(bird_id,nick_name,taxon,id,ring_id,taxon_eng,taxon_fr,date_start,date_end,number_of_events,nb_day_silence,new,import_date)]
my_kable_print( ind_select,caption="The birds",scroll_width = "600px")
```

## The events

The events correspond to the whole bird's location get from movebank. 

```{r movebankdata_envents}
my_kable_print(d[1:20,],caption="The event data",scroll_width = "600px")
```




