---
title: "**Importing Kivikuaka's data from movebank**"
author: Romain Lorrilliere\thanks{\href{mailto:romain.lorrilliere@mnhn.fr}{\textit{romain.lorrilliere@mnhn.fr}}}
date: "`r format(Sys.time(), '%d/%m/%Y')`"
output:
  html_document:
    df_print: paged
    fig_height: 12
    fig_width: 16
    toc: yes
    toc_depth: 3
    toc_float:
      collapsed: true
      smooth_scroll: false
    number_sections: true
    code_folding: hide
pdf_document:
  toc: yes
  toc_depth: '1'
params: 
   set_rep: "C:/git/KiviKuaka/"
   set_file_data: "data/data_kivikuaka_events.csv"
   set_mb_pw: "xxx"
   set_mb_user: "romainlorrilliere"
   set_save_fig: FALSE 
---

```{r setup, include=FALSE}

knitr::opts_chunk$set(echo =TRUE, eval=TRUE, message = FALSE, warning = FALSE,cache=FALSE)

```


```{r param_test}

rep <- params$set_rep
file_data <- params$set_file_data
pw <- params$set_mb_pw
username <- params$set_mb_user
save.fig <- params$set_save_fig

```




```{r changeRep}

knitr::opts_knit$set(root.dir = rep)
#setwd("..")

```


```{r source}

file_source <- paste0(rep,"functions/fun_rmd_generic.r")
source(file_source)
file_source <- paste0(rep,"functions/fun_importation.r")
source(file_source)



```


# Get data from movebank



```{r movebank_log}

if(pw == "xxx"){
    file <- paste0(rep,"data/pw.txt")
    pw <- get_pw(file)
}
log <- movebankLogin(username,pw)
```


```{r save_previous_db}

``` 


```{r last_date_import}

last_import_date <- NULL
difftime_last_import <- NULL
txt_last_import <- "This is the first data importing."

if(basename(file_data) %in% dir(paste0(rep,"data/"))) {
  dlast <- fread(paste0(rep,file_data))
  if("db_date" %in% colnames(dlast)) { 
    last_import_date <- dlast[1,db_date] 
    difftime_last_import <- difftime(Sys.time(),last_import_date,units = "day")
    txt_last_import <- paste0("Date of the previous data update: ",last_import_date," (",difftime_last_import," day(s))\n")
  } 
  file_save <- paste0(rep,"/",file_path_sans_ext(file_data),"_last",ifelse(is.null(last_import_date),"",paste0("_",last_import_date)),".csv")
  fwrite(dlast,file_save)
}

```


`r txt_last_import`


```{r movebank_import}
ind <- get_birds(log)
d <- get_events(log)
```



## The birds


```{r movebankdata_ind}
ind_select <- ind[,.(bird_id,nick_name,taxon,id,ring_id,taxon_eng,taxon_fr,date_start,date_end,number_of_events,nb_day_silence,new,import_date)]
my_kable_print( ind_select,caption="The birds",scroll_width = "600px")
```

## The events

The events correspond to the whole bird's location get from movebank. 

```{r movebankdata_envents}
my_kable_print(d[1:100,],caption="The event data",scroll_width = "600px")
```


# Summary of data

## The birds


In French Polynesia, we deployed Icarus GPS 5g beacon on 56 birds of four species, three shorebirds (13 Bristle-thighed Curlew, 8 Pacific Golden Plover, 23 Wandering Tattler), and 12 Sooty Tern. 



```{r summary_ind}
summary_ind <- summary_new_ind(ind)

nb_birds <- sum(summary_ind$nb_birds)

nb_birds_5days <- sum(summary_ind$nb_birds_5days)
nb_birds_10days <- sum(summary_ind$nb_birds_10days)

prop_5days <-  round(nb_birds_5days/nb_birds,2)
prop_10days <- round(nb_birds_10days/nb_birds,2)

my_kable_print(summary_ind,caption="The summary of number of birds",scroll_width = "600px",scroll=FALSE)

```



Among these 56 birds, __$`r nb_birds`$__ birds with Icarus GPS beacons sent to at least one location. In the last five days, __$`r nb_birds_10days`$__ beacons ($`r round(prop_10days*100)`\%$) sent data, and for the last five days, __$`r nb_birds_5days`$__ beacons ($`r round(prop_5days*100)`\%$).

There would seem to be a species effect on the time since the last location. 


```{r fig.silence, fig.width=7, fig.height=7,eval=TRUE,fig.align = 'center', out.width='70%',fig.cap="Distrubiton of the number of days before after location by species",fig.scap="number of days before after location"}
ggplot_silence(ind)
```


## The new events


```{r summary_events}
nbline <- nrow(d)
nbloc <- nrow(d[!(is.na(location_lat))])

d_tax <- fread(paste0(rep,"data/taxon.csv"))
vec_tax_eng <- d_tax[taxon %in% unique(d$taxon),taxon_eng]
vec_tax<- d_tax[taxon %in% unique(d$taxon),taxon]

```

In the events database, there are $`r nbline`$ data, but some do not have a valid location. 
There are __$`r nbloc`$__ data with location, that corresponds to $`r round(nbloc/nbline * 100)`\%$.


```{r summary_new_events}
  sne <- summary_new_events(d)
if(is.null(sne)) nb_new <- 0 else nb_new <- sum(sne$nb_new_events)
```

There `r ifelse(nb_new<1,"is","are")` __$`r nb_new`$__ new data since the last update `r ifelse(is.null(difftime_last_import),"",paste0())`. 


```{r summary_new_events_table,eval=FALSE, include=FALSE}
if(!(is.null(sne)))
  my_kable_print(sne,caption="The new events",scroll_width = "600px")
```

## The events by day

```{r title_fig_bird_day}
  cap_txt <- paste0("The bird locations by day for the ",vec_tax_eng)
```


```{r bird_day,fig.width=9, fig.height=12,eval=TRUE,fig.align = 'center', out.width='100%', fig.cap=cap_txt}
data_by_day(d,ind,vec_tax)
```



